Title here

### 2020-08-31 paper/paper.Rmd
changes on the plot definition, good vs. bad plots

```{r toy-search, fig.height=3, fig.cap="\\label{toy-search}A comparison of plotting the same search points with different plot designs. In the upper plot, points from the last three iterations span the vast majority of the plotting space leaving the first few iterations being squeezed together whilst the lower plot spaces each iteration evenly and presents summary information easy to read."}

@@

p1 <- dt %>% explore_trace_search()

p1

@@

p1 <- interp %>% 
  ggplot(aes(x = id, y = index_val, col = as.factor(tries))) + 
  geom_point() + 
  geom_line() + 
  theme(legend.position = "bottom")

p2 <- interrupt_no %>% explore_trace_interp() + 
  theme(legend.position = "bottom")

p3 <- holes_2d_better_random %>% explore_trace_interp() + 
  theme(legend.position = "bottom")

@@

```{r toy-pca, fig.height = 4, fig.cap = "\\label{toy-pca}PCA plot of search geodesic colouring by info allows for better understanding of each stage in the geodesic search"}

holes_1d_geo %>% explore_proj_pca(col = info)

>>>>

```{r toy-search, fig.height=5.5, fig.cap="\\label{toy-search}A comparison of plotting the same search points with different plot designs. In the upper plot, points from the last three iterations span the vast majority of the plotting space leaving the first few iterations being squeezed together whilst the lower plot spaces each iteration evenly and presents summary information easy to read."}

@@

p1 <- dt %>% explore_trace_search() + 
  ggtitle("satisfactory")

p2 <- holes_2d_better %>% explore_trace_search() + 
  ggtitle("not satisfactory")

p1 / p2

@@

p1 <- interp %>% 
  ggplot(aes(x = id, y = index_val, col = as.factor(tries))) + 
  geom_point() + 
  geom_line() + 
  theme(legend.position = "bottom") + 
  ggtitle("satisfactory")

p2 <- interrupt_no %>% explore_trace_interp() + 
  theme(legend.position = "bottom") + 
  ggtitle("not satisfactory")

p3 <- holes_2d_better_random %>% explore_trace_interp() + 
  theme(legend.position = "bottom") + 
  ggtitle("maybe satisfactory?")

@@

```{r toy-pca, fig.height = 6, fig.cap = "\\label{toy-pca}PCA plot of search geodesic colouring by info allows for better understanding of each stage in the geodesic search"}
# holes_1d_geo %>% explore_proj_pca(col = info) 
# holes_1d_better%>% explore_proj_pca(col = info) 
# 
# bind_rows(holes_1d_geo, holes_1d_better) %>% explore_proj_pca(col = method)
# 
# 
# dt <- bind_rows(holes_1d_better, holes_1d_geo) %>% 
#   compute_pca() %>% 
#   `$`(combined)
# 
# last <- dt %>% 
#   filter(info == "interpolation") %>% 
#     group_by(method) %>% 
#   filter(id == max(id))
# 
# start <- dt %>% filter(id == 1)
# 
# dt %>% 
#   ggplot(aes(x = PC1, y = PC2, col = info)) + 
#   geom_point() + 
#   #facet_wrap(vars(method)) + 
#   theme(aspect.ratio = 1, legend.position = "bottom") + 
#   geom_point(data = last, size = 7) + 
#   geom_point(data = start, size = 7)
# 
# 
# bind_rows(holes_1d_better, holes_1d_geo) %>%
#   filter(info == "interpolation") %>%
#   group_by(method) %>%
#   mutate(id = row_number()) %>%
#   ggplot(aes(x = id, y = index_val, group = method, col = as.factor(tries))) +
#   geom_point() +
#   geom_line() +
#   facet_wrap(vars(method), ncol = 2)
# 
# ######
# dt <- bind_rows(holes_2d_better, holes_2d_geo) %>% 
#   compute_pca() %>% 
#   `$`(combined)
# 
# last <- dt %>% 
#   filter(info == "interpolation") %>% 
#     group_by(method) %>% 
#   filter(id == max(id))
# 
# start <- dt %>% filter(id == 1)
# 
# dt %>% filter(!is.na(info)) %>% 
#   ggplot(aes(x = PC1, y = PC2, col = info)) + 
#   geom_point() + 
#   geom_point(data = last, size = 7) + 
#   geom_point(data = start, size = 7) + 
#   facet_wrap(vars(method)) + 
#   theme(aspect.ratio = 1, legend.position = "bottom")

#####
dt <- bind_rows(holes_2d_better %>% mutate(algo = "not satisfactory"), holes_2d_better_max_tries %>% mutate(algo = "satisfactory")) %>% mutate(info = ifelse(info == "start", "new_basis", info)) %>% 
  compute_pca() %>% 
  `$`(combined)

last <- dt %>% 
  filter(info == "interpolation") %>% 
  group_by(algo) %>% 
  filter(id == max(id))

start <- dt %>% filter(id == 1)

dt %>% filter(!is.na(info)) %>% 
  ggplot() + 
  geom_point(aes(x = PC1, y = PC2, col = info)) + 
  geom_point(data = last, aes(x = PC1, y = PC2, col = info), size = 7) + 
  geom_point(data = start,aes(x = PC1, y = PC2, col = info), size = 7) + 
  facet_wrap(vars(algo)) + 
  theme(aspect.ratio = 1, legend.position = "bottom")

# bind_rows(holes_2d_better, holes_2d_geo) %>% 
#   filter(info == "interpolation") %>% 
#   group_by(method) %>% 
#   mutate(id = row_number()) %>% 
#   ggplot(aes(x = id, y = index_val, group = method, col = as.factor(tries))) + 
#   geom_point() + 
#   geom_line() + 
#   facet_wrap(vars(method), ncol = 1)

#holes_2d_geo %>% explore_trace_interp()
